{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
update to Slides for GPM

\begin{frame}{LSN \textit{vs} Double null on TCV}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}{LSN \textit{vs} Double null on TCV}
%  \begin{columns}
%    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=.6\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
      \centering{\includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58624}}
      \centering{\includegraphics<4>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
%    \end{column}
%    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item<1|only@1> Comparing similar L-Mode density ramp at same
          current in LSN and DN with ion $\mathbf{B}\times\nabla B$
          pointing towards the floor. Lower ion flux to lower target
          observed in DN and profiles before rollover seem more broad
          in LSN. After rollover the profiles are actually similar
      \item<2|only@2>  From bolometry we can observe an
          unbalanced movement of the radiation front suggesting a non
          perfectly balanced DN
      \item<3|only@3> This is confirmed at higher current where the
        more active X-point is the upper one with a consequent higher
        radiation from bolometry chords    
      \end{itemize}
%    \end{column}
%  \end{columns}
\end{frame}
